---
title: "Webexercises"
---

```{r, echo = FALSE, results='asis'}
knitr::opts_chunk$set(echo = FALSE)

# Uncomment to change widget colours:
#style_widgets(incorrect = "goldenrod", correct = "purple", highlight = "firebrick")
```

This is a Web Exercise template created by the [psychology teaching team
at the University of Glasgow](http://www.psy.gla.ac.uk), based on ideas
from [Software Carpentry](https://software-carpentry.org/lessons/). This
template shows how instructors can easily create interactive web
documents that students can use in self-guided learning.

The `{webexercises}` package provides a number of functions that you use
in [inline R
code](https://github.com/rstudio/cheatsheets/raw/master/rmarkdown-2.0.pdf)
or through code chunk options to create HTML widgets (text boxes, pull
down menus, buttons that reveal hidden content). Examples are given
below. Render this file to HTML to see how it works.

**NOTE: To use the widgets in the compiled HTML file, you need to have a
JavaScript-enabled browser.**

## Example Questions

### Fill-In-The-Blanks (`fitb()`)

Create fill-in-the-blank questions using `fitb()`, providing the answer
as the first argument.

-   2 + 2 is `r fitb(4)`

You can also create these questions dynamically, using variables from
your R session.

```{r}
x <- sample(2:8, 1)
```

-   The square root of `r x^2` is: `r fitb(x)`

The blanks are case-sensitive; if you don't care about case, use the
argument `ignore_case = TRUE`.

-   What is the letter after D? `r fitb("E", ignore_case = TRUE)`

If you want to ignore differences in whitespace use, use the argument
`ignore_ws = TRUE` (which is the default) and include spaces in your
answer anywhere they could be acceptable.

-   How do you load the tidyverse package?
    `r fitb(c("library( tidyverse )", "library( \"tidyverse\" )", "library( 'tidyverse' )"), ignore_ws = TRUE, width = "20")`

You can set more than one possible correct answer by setting the answers
as a vector.

-   Type a vowel:
    `r fitb(c("A", "E", "I", "O" , "U"), ignore_case = TRUE)`

You can use regular expressions to test answers against more complex
rules.

-   Type any 3 letters:
    `r fitb("^[a-zA-Z]{3}$", width = 3, regex = TRUE)`

### Multiple Choice (`mcq()`)

-   "Never gonna give you up, never gonna:
    `r mcq(c("let you go", "turn you down", "run away", answer = "let you down"))`"
-   "I
    `r mcq(c(answer = "bless the rains", "guess it rains", "sense the rain"))`
    down in Africa" -Toto

### True or False (`torf()`)

-   True or False? You can permute values in a vector using `sample()`.
    `r torf(TRUE)`

### Longer MCQs (`longmcq()`)

When your answers are very long, sometimes a drop-down select box gets
formatted oddly. You can use `longmcq()` to deal with this. Since the
answers are long, It's probably best to set up the options inside an R
chunk with `echo=FALSE`.

**What is a p-value?**

```{r}
opts_p <- c(
   "the probability that the null hypothesis is true",
   answer = "the probability of the observed, or more extreme, data, under the assumption that the null-hypothesis is true",
   "the probability of making an error in your conclusion"
)
```

`r longmcq(opts_p)`

**What is true about a 95% confidence interval of the mean?**

```{r}
# use sample() to randomise the order
opts_ci <- sample(c(
  answer = "if you repeated the process many times, 95% of intervals calculated in this way contain the true mean",
  "there is a 95% probability that the true mean lies within this range",
  "95% of the data fall within this range"
))
```

`r longmcq(opts_ci)`

## Checked sections

Create sections with the class `webex-check` to add a button that hides
feedback until it is pressed. Add the class `webex-box` to draw a box
around the section (or use your own styles).

::: {.webex-check .webex-box}
I am going to learn a lot: `r torf(TRUE)`

```{r, results='asis'}
opts <- c(
   "the probability that the null hypothesis is true",
   answer = "the probability of the observed, or more extreme, data, under the assumption that the null-hypothesis is true",
   "the probability of making an error in your conclusion"
)

cat("What is a p-value?", longmcq(opts))
```
:::

## Hidden solutions and hints

You can fence off a solution area that will be hidden behind a button
using `hide()` before the solution and `unhide()` after, each as inline
R code. Pass the text you want to appear on the button to the `hide()`
function.

If the solution is a code chunk, instead of using `hide()` and
`unhide()`, simply set the `webex.hide` chunk option to TRUE, or set it
to the string you wish to display on the button.

**Recreate the scatterplot below, using the built-in `cars` dataset.**

```{r}
with(cars, plot(speed, dist))
```

`r hide("I need a hint")`

See the documentation for `plot()` (`?plot`)

`r unhide()`

<!-- note: you could also just set webex.hide to TRUE -->

```{r, echo = TRUE, eval = FALSE}
#| webex.hide: "Click here to see the solution"
plot(cars$speed, cars$dist)
```

---
title: "Psychology of Deception: Web Exercises"
---

```{r, echo = FALSE, results='asis'}
knitr::opts_chunk$set(echo = FALSE)
```

This set of exercises will test your knowledge about various aspects of
deception in psychology. Answer the questions to check your
understanding of key concepts, theories, and research findings in this
area.

## Fill-In-The-Blanks

1.  The tendency for people to believe they are less likely to be
    deceived than others is known as the
    `r fitb(c("illusion of invulnerability", "invulnerability illusion"), ignore_case = TRUE)`
    to deception.

2.  In deception research, the
    `r fitb("confederate", ignore_case = TRUE)` is an actor who works
    with the experimenter to deceive the actual participant.

3.  The `r fitb(c("Duchenne smile", "Duchenne"), ignore_case = TRUE)` is
    a genuine smile that involves both the mouth and the eyes, making it
    harder to fake in deceptive situations.

## Multiple Choice

1.  Which of the following is NOT typically considered a reliable
    indicator of deception?

`r mcq(c("Increased blinking", "Reduced hand gestures", answer = "Lack of eye contact", "Increased speech errors"))`

2.  The theory that proposes that lying is more cognitively demanding
    than telling the truth is called:

`r mcq(c("Interpersonal Deception Theory", answer = "Cognitive Load Theory", "Four-Factor Theory", "Self-Presentation Theory"))`

3.  In a typical deception study, who is usually unaware of the true
    nature of the experiment?

`r mcq(c(answer = "Participant", "Experimenter", "Confederate", "Research Assistant"))`

## True or False

1.  Polygraph tests are highly accurate and widely accepted in
    scientific communities as reliable lie detectors. `r torf(FALSE)`

2.  People are generally better at detecting lies told by strangers than
    by those close to them. `r torf(FALSE)`

3.  Microexpressions are brief, involuntary facial expressions that can
    potentially reveal concealed emotions in deceptive situations.
    `r torf(TRUE)`

## Longer MCQs

**Which of the following best describes the "Truth-Default Theory" in
deception research?**

```{r}
opts_tdt <- c(
   "The theory that humans are naturally inclined to always tell the truth",
   answer = "The theory that humans tend to believe others are telling the truth unless given reason to think otherwise",
   "The theory that truth-telling is easier and requires less cognitive effort than lying",
   "The theory that cultural norms universally prioritize truthfulness over deception"
)
```

`r longmcq(opts_tdt)`

**What is the primary focus of Interpersonal Deception Theory (IDT)?**

```{r}
opts_idt <- sample(c(
  answer = "The dynamic interaction between the deceiver and the target of deception",
  "The psychological motivations that drive individuals to engage in deceptive behavior",
  "The neurological processes involved in creating and maintaining a lie",
  "The cultural variations in perceptions and acceptance of deceptive practices"
))
```

`r longmcq(opts_idt)`

## Checked sections

::: {.webex-check .webex-box}
Research suggests that detecting deception is:

`r mcq(c("Easy for most people", "Only possible with specialized training", answer = "Difficult, with accuracy rates often only slightly above chance", "Impossible without technological aids"))`

Explain why detecting deception is challenging for most people:

`r hide("Click for explanation")`

Detecting deception is challenging for several reasons:

1.  Many common beliefs about deception cues (e.g., lack of eye contact)
    are not reliable indicators.
2.  Liars often strategically control their behavior to appear truthful.
3.  Individual differences in baseline behavior make it hard to identify
    deviations.
4.  The cognitive load of trying to detect lies can impair judgment.
5.  Confirmation bias can lead people to interpret ambiguous cues in
    line with their expectations.

`r unhide()`
:::

## Hidden solutions and hints

**A researcher wants to study how cognitive load affects lying behavior.
Describe a potential experimental design to investigate this.**

`r hide("I need a hint")`

Consider how you might manipulate cognitive load (e.g., through a
secondary task) and measure lying behavior. Think about what control
conditions you might need.

`r unhide()`

```{r, echo = TRUE, eval = FALSE}
#| webex.hide: "Click here to see a possible experimental design"
# Possible Experimental Design:

# Participants: 100 adults randomly assigned to two groups (50 each)
# 
# Procedure:
# 1. All participants are asked to lie about a recent experience
# 
# 2. Experimental group: 
#    - Must count backwards from 100 by 7s while lying (high cognitive load)
# 
# 3. Control group:
#    - Simply lie without additional task (normal cognitive load)
# 
# 4. Measure dependent variables:
#    - Speech hesitations
#    - Speech rate
#    - Amount of detail provided
#    - Perceived believability (rated by independent judges)
# 
# 5. Compare measures between groups to assess the effect of cognitive load on lying behavior

# This design allows us to isolate the effect of increased cognitive load on various aspects of lying behavior.
```

This set of exercises covers various aspects of deception psychology,
including theories, research methods, and key findings. It utilizes
different question types to engage learners and test their understanding
of the subject matter.
