---
title: PS53011C/PS71020E Lab Worksheet
format: 
  html:
    code-tools: true
    code-overflow: wrap
    code-annotations: hover
    code-block-bg: true
    code-block-border-left: true
    toc: true
    number-sections: true
    df-print: kable

execute:
  echo: true
  warning: false
  message: false
  error: true
---

::: {.panel-tabset}

### 📊 Lab Instructions

This week's lab will explore multiple regression using tidyverse principles!

---

### 📽️ Slides


<div style="position: relative; padding-top: 56.25%; height: 0; overflow: hidden;">
  <iframe src="lab_slides.html" 
          style="position: absolute; top: 0; left: 0; width: 100%; height: 100%; border: none;"
          allowfullscreen
          loading="lazy">
  </iframe>
</div>

> 🧭 **These are your slides for the week!**
>
> Use the arrow keys to navigate through the slides:
>
> - ⬅️ and ➡️ to move left and right
> - ⬆️ and ⬇️ for nested (vertical) slides
> - Press `Esc` to view the **slide overview**
> - Press `F` for **fullscreen** (or use browser controls)
> - Press `O` to toggle the **overview mode**
> - Press `S` to open the **Speaker Notes** window (in presenter mode)
>
> 💡 Slides are best viewed in **fullscreen** for clarity.

:::


## Week 4: Multiple Regression (Part 1)

> Please attempt all questions in your own words. Model answers will be available on the VLE page following the lab session.

---

::: {.learning-outcomes #sec-lab01-LO}
## Learning Outcomes

1. Conduct simple and multiple linear regression analyses using R and the Tidyverse.  
2. Explore relationships between regression coefficients and correlation measures.  
3. Assess assumptions of linear regression including normality, linearity, and multicollinearity.  
4. Compute and interpret simple, partial, and semipartial correlations in R.
:::

---

## Materials

- **Software**: R (Tidyverse package)
- **Dataset**: {{< downloadthis data/fearful_faces.csv dname=fearful_faces label="Download the fearful_faces data" icon=database-fill-down type=info class=data-button id=fearful_faces >}}

```{r}
#| label: load-libraries
#| message: false
#| warning: false
library(tidyverse)
```

---

## Dataset Overview

The dataset includes reaction time (RT) data for participants responding to emotional facial expressions. Of particular interest is the average RT to fearful faces for correct identifications. Predictors include:

- `traitanx`: Trait anxiety (Spielberger scale)
- `ACS`: Attentional Control Scale score
- `Age`: Participant age

---

## Task 1: Descriptive Statistics and Visualisation

- Load the dataset
- Create summary statistics and visualizations for RT, traitanx, ACS, and Age.

```{r}
#| label: descriptives
fearful_data <- read_csv("data/fearful_faces.csv")

fearful_data %>%
  summarise(across(c(Fearful_face_RT, Happy_face_RT, traitanx, ACS, Age), list(mean = mean, sd = sd), na.rm = TRUE))

fearful_data %>%
  pivot_longer(cols = c(Fearful_face_RT, Happy_face_RT, traitanx, ACS, Age), names_to = "variable", values_to = "value") %>%
  ggplot(aes(x = value)) +
  geom_histogram(bins = 30, fill = "steelblue", color = "white") +
  facet_wrap(~ variable, scales = "free") +
  theme_minimal()
```

---

## Task 2: Correlation Analysis

- Compute a correlation matrix
- Visualize relationships using scatterplots

```{r}
#| label: correlations
fearful_data %>%
  select(Fearful_face_RT, Happy_face_RT, traitanx, ACS, Age) %>%
  cor(use = "complete.obs") %>%
  round(2)

pairs(fearful_data %>% select(Fearful_face_RT, Happy_face_RT, traitanx, ACS, Age), main = "Scatterplot Matrix")
```

---

## Task 3: Multiple Regression

- Conduct a multiple regression predicting Fearful_face_RT from traitanx, ACS, and Age.

```{r}
#| label: regression-model
model <- lm(Fearful_face_RT ~ traitanx + ACS + Age, data = fearful_data)
summary(model)
```

---

## Task 4: Model Diagnostics

- Check linear regression assumptions.

```{r}
#| label: diagnostics
par(mfrow = c(2, 2))
plot(model)
```

---

## Task 5: Partial and Semipartial Correlations

```{r}
#| label: part-corr
#| #| message: false
#| warning: false

# Load required libraries
library(tidyverse)
library(ppcor)


# Calculate partial correlations
partial_data <- fearful_data %>%
  dplyr::select(Fearful_face_RT, traitanx, ACS, Age) %>%
  drop_na()
pcor_result <- pcor(partial_data, method = "pearson")
pcor_result
```

---

## Task 6: Semipartial (Part) Correlation

> This task explores how to isolate the unique contribution of one predictor (e.g., trait anxiety) to a dependent variable (reaction time), controlling for other variables only in the predictor.

### Objective
- Calculate a semipartial correlation between `Fearful_face_RT` and `traitanx`, controlling for `ACS` and `Age` **only in the predictor**.

```{r}
#| label: semipartial-correlation
#| message: false
#| warning: false

# Load tidyverse if not already
library(tidyverse)

# Ensure your data is clean
semipartial_data <- fearful_data %>%
  dplyr::select(Fearful_face_RT, traitanx, ACS, Age) %>%
  drop_na()

# Step 1: Residualize the predictor (traitanx ~ ACS + Age)
resid_traitanx <- lm(traitanx ~ ACS + Age, data = semipartial_data)$residuals

# Step 2: Compute correlation between raw DV and residualized predictor
semipartial_corr <- cor(semipartial_data$Fearful_face_RT, resid_traitanx)
semipartial_corr
```

::: {.callout-note}
**Interpretation:** This semipartial correlation represents the unique association between trait anxiety and fearful face reaction time, controlling for ACS and Age **only in trait anxiety**. Unlike partial correlation, it leaves the DV unadjusted.
:::

---

## Reflection

- How does anxiety influence reaction time to fearful faces?
- Does attentional control modify this relationship?
- Are the findings specific to fearful stimuli, or would they generalize to other emotional expressions?

> Review your code and interpretations. Cross-reference with theoretical models on anxiety and attentional control.

