---
title: "Lab Worksheet: Multiple Regression (Part 1)"
author: "PS53011C/PS71020E"
format: html
---

# PS53011C/PS71020E Lab Worksheet

## Week 4: Multiple Regression (Part 1)

> Please attempt all questions in your own words. Model answers will be available on the VLE page following the lab session.

---

## Learning Outcomes

1. Conduct simple and multiple linear regression analyses using R and the Tidyverse.
2. Explore relationships between regression coefficients and correlation measures.
3. Assess assumptions of linear regression including normality, linearity, and multicollinearity.
4. Compute and interpret simple, partial, and semipartial correlations in R.

---

## Materials

- **Software**: R (Tidyverse package)
- **Dataset**: [Download week4_fearful_faces.csv](downloadthis::data/fearful_faces.csv)

```{r}
#| label: load-libraries
#| message: false
#| warning: false
library(tidyverse)
```

---

## Dataset Overview

The dataset includes reaction time (RT) data for participants responding to emotional facial expressions. Of particular interest is the average RT to fearful faces for correct identifications. Predictors include:

- `traitanx`: Trait anxiety (Spielberger scale)
- `ACS`: Attentional Control Scale score
- `age`: Participant age

---

## Task 1: Descriptive Statistics and Visualisation

- Load the dataset
- Create summary statistics and visualizations for RT, traitanx, ACS, and age.

```{r}
#| label: descriptives
fearful_data <- read_csv("data/fearful_faces.csv")

fearful_data %>%
  summarise(across(c(RT, traitanx, ACS, age), list(mean = mean, sd = sd), na.rm = TRUE))

fearful_data %>%
  pivot_longer(cols = c(RT, traitanx, ACS, age), names_to = "variable", values_to = "value") %>%
  ggplot(aes(x = value)) +
  geom_histogram(bins = 30, fill = "steelblue", color = "white") +
  facet_wrap(~ variable, scales = "free") +
  theme_minimal()
```

---

## Task 2: Correlation Analysis

- Compute a correlation matrix
- Visualize relationships using scatterplots

```{r}
#| label: correlations
fearful_data %>%
  select(RT, traitanx, ACS, age) %>%
  cor(use = "complete.obs") %>%
  round(2)

pairs(fearful_data %>% select(RT, traitanx, ACS, age), main = "Scatterplot Matrix")
```

---

## Task 3: Multiple Regression

- Conduct a multiple regression predicting RT from traitanx, ACS, and age.

```{r}
#| label: regression-model
model <- lm(RT ~ traitanx + ACS + age, data = fearful_data)
summary(model)
```

---

## Task 4: Model Diagnostics

- Check linear regression assumptions.

```{r}
#| label: diagnostics
par(mfrow = c(2, 2))
plot(model)
```

---

## Task 5: Partial and Semipartial Correlations

```{r}
#| label: part-corr
library(ppcor)
pcor_result <- pcor(fearful_data %>% select(RT, traitanx, ACS, age), method = "pearson")
pcor_result
```

---

## Reflection

- How does anxiety influence reaction time to fearful faces?
- Does attentional control modify this relationship?
- Are the findings specific to fearful stimuli, or would they generalize to other emotional expressions?

> Review your code and interpretations. Cross-reference with theoretical models on anxiety and attentional control.

