---
title: "codeoptions"
subtitle: A Year 1 Textbook Chapter
format:
  html: default
code-annotations: hover
execute: 
  warning: false
---

## Version 1 - Chunk Fold with line numbers

```{r}
#| code-fold: true
#| code-summary: "Show the code"
#| code-line-numbers: true

library(tidyverse)
library(palmerpenguins)
penguins |>                                      # <1>
  mutate(                                        # <2>
    bill_ratio = bill_depth_mm / bill_length_mm, # <2>
    bill_area  = bill_depth_mm * bill_length_mm  # <2>
  ) 
```

1.  Take `penguins`, and then,
2.  add new columns for the bill ratio and bill area.

## Version 2 - Standard Tabset with code and Code Yoda

::: panel-tabset
## Code

```{r}
library(tidyverse)
library(palmerpenguins)
penguins |>                                     
  mutate(                                       
    bill_ratio = bill_depth_mm / bill_length_mm,
    bill_area  = bill_depth_mm * bill_length_mm 
  )

```

## CodeYoda (#\| eval: false)

```{r}
#| eval: false
library(tidyverse)
library(palmerpenguins)
penguins |>                                      # <1>
  mutate(                                        # <2>
    bill_ratio = bill_depth_mm / bill_length_mm, # <2>
    bill_area  = bill_depth_mm * bill_length_mm  # <2>
  )
```

1.  Take `penguins`, and then,
2.  add new columns for the bill ratio and bill area.
:::

## Version 3 - Panelize and Webr (coatless) and can't seem to get annotations to work (echo:false for R)

::: to-webr
```{r}

library(tidyverse)
library(palmerpenguins)
penguins |>                                     
  mutate(                                       
    bill_ratio = bill_depth_mm / bill_length_mm,
    bill_area  = bill_depth_mm * bill_length_mm 
  )         
```
:::

## Version 4 - Just trying to get the Code annotations to work (#\| eval: false)

```{r}
#| eval: false
library(tidyverse)
library(palmerpenguins)
penguins |>                                      # <1>
  mutate(                                        # <2>
    bill_ratio = bill_depth_mm / bill_length_mm, # <2>
    bill_area  = bill_depth_mm * bill_length_mm  # <2>
  )
```

1.  Take `penguins`, and then,
2.  add new columns for the bill ratio and bill area.

# Embedding pdf

## Native Quarto

![](assets/dummypdf.pdf)

## With size spec ![](assets/dummypdf.pdf){width="60%" height="400"}

## With embedpdf extension x3 from raw file
{{< pdf ./assets/dummypdf.pdf >}}

raw file with size options
{{< pdf ./assets/dummypdf.pdf width=100% height=800 >}}

url with ""
{{< pdf "https://proceedings.neurips.cc/paper_files/paper/2017/file/3f5ee243547dee91fbd053c1c4a845aa-Paper.pdf" >}}
<<<<<<< HEAD

{{< pdf "https://interrm.littlemonkeylab.com/week01/data/dummypdf.pdf" >}}
=======
>>>>>>> 945ad51f57d64470c9643cb73b8bd6151555b866
